---
title: "ENPOL_Graphs"
author: "Eduardo Zago"
date: "24/5/2022"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, include=FALSE, echo=FALSE}
library(haven)
library(tidyverse)
library(sandwich)
library(stargazer)
library(fixest)
library(knitr)
library(RCT)
library(kableExtra)
library(ggpubr)
```

```{r functions}
no_sabe_toNA <- function(x) ifelse(x == 8 | x == 9, NA, x)

no_responde_toNA <- function(x) ifelse(x == 99 | x == 98, NA, x)

tab <- function(frame_x, var_name){
     var_name <- enquo(var_name)
     frame_x |>
          group_by(!!var_name) |>
          summarise(n = n()) |>
          mutate(totalN = (cumsum(n)),
                 percent = round((n / sum(n)), 3),
                 cumuPer = round(cumsum(freq = n / sum(n)), 3))
}

dummies <- function(x) ifelse(x == 2, 0, x)
```


```{r, include=FALSE}
# Paths
path_in <- "C:/Users/lalo-/Dropbox/Research/Prisons/Tesis/data/clean/"
path_out <- "C:/Users/lalo-/Dropbox/Research/Prisons/Tesis/data/clean/csvs/"
path_results <- "C:/Users/lalo-/Dropbox/Research/Prisons/Tesis/results/"
```

```{r}
# Importing the output (run from here if you do not want to run all the code from above)
controls_final <- read.csv(paste0(path_out, "controls.csv"))
crime <- read.csv(paste0(path_out, "crimes.csv"))
```

# Preparation


# Results:

Now we can generate relevant descriptive statistics for each group: Private and Public. For example, we might be interested in the mean of both groups, as well as the p-value from a t-test, to see if they are similar or not:

Personal Characteristics (gender, sexual orientation, race, age)
```{r, results = "include"}
controls_final %>% 
  select(private, age, school, dialect, lit_read, lit_write,
         afro:other_race, cis, trans, bi:other_sexor) %>%
  balance_table(., "private") %>%
  rename(variables = variables1,
         m_public = Media_control1,
         m_private = Media_trat1,
         p_value = p_value1) %>%
  kable(col.names = c("Variables",
                      "Public", 
                      "Private", "P-value"), format = "latex",
        booktabs = T, 
        caption = "Balance Table: Personal Characteristics")
```
Household characteristics (marital status, children):

```{r, results = "include"}
controls_final %>% 
  select(private, married:widower, child:agechild3) %>%
  balance_table(., "private") %>%
  rename(variables = variables1,
         m_public = Media_control1,
         m_private = Media_trat1,
         p_value = p_value1) %>%
  kable(col.names = c("Variables",
                      "Public", 
                      "Private", "P-value"), format = "latex",
        booktabs = T, 
        caption = "Balance Table: Household Characteristics")
```

Health and Drug Consumption:

```{r, results = "include"}
controls_final %>% 
  select(private, diabetes:Drugs) %>%
  balance_table(., "private") %>%
  rename(variables = variables1,
         m_public = Media_control1,
         m_private = Media_trat1,
         p_value = p_value1) %>%
  kable(col.names = c("Variables",
                      "Public", 
                      "Private", "P-value"), format = "latex",
        booktabs = T,
        caption = "Balance Table: Health and Drug Abuse")
```

Prior Work Characteristics and Sentences:

```{r, results = "include"}
controls_final %>% 
  select(private, time_inc:housing_prior, re_offender) %>%
  balance_table(., "private") %>%
  rename(variables = variables1,
         m_public = Media_control1,
         m_private = Media_trat1,
         p_value = p_value1) %>%
  kable(col.names = c("Variables",
                      "Public", 
                      "Private", "P-value"), format = "latex",
        booktabs = T,
        caption = "Balance Table: Prior Characteristics")
```

Relevant 0nes

```{r, results = asis}
table <- controls_final %>% 
  select(private, age, children, school, lit_read,
         lit_write, single, married, sentence, income_prior) %>%
  balance_table(., "private") %>%
  rename(variables = variables1,
         m_public = Media_control1,
         m_private = Media_trat1,
         p_value = p_value1)

kbl(table, col.names = c("Variables",
                      "Public", 
                      "Private", "P-value"),
        format = "latex",
        caption = "Table 1. Balance Table",
        booktabs = T)
```

Crimes:


```{r}
crime %>% 
  select(private, rape.x:org_crime.x) %>%
  balance_table(., "private") %>%
  rename(variables = variables1,
         m_public = Media_control1,
         m_private = Media_trat1,
         p_value = p_value1) %>%
  mutate(across(where(is.numeric), ~ round(.x, digits = 4))) %>%
  kable(col.names = c("Variables",
                      "Public", 
                      "Private", "P-value"), format = "latex",
        booktabs = T,
        caption = "Balance Table: Prior Characteristics")
```

```{r}
crime %>% 
  select(private, rape.y:org_crime.y) %>%
  balance_table(., "private") %>%
  rename(variables = variables1,
         m_public = Media_control1,
         m_private = Media_trat1,
         p_value = p_value1)
```



# Graphs

```{r}
# Importing the output (run from here if you do not want to run all the code from above)
dep_rates <- read.csv(paste0(path_out, "dependent_rates.csv"))
```

```{r}
dep_rates_longer <- dep_rates |> pivot_longer(cols = starts_with("rate"), names_to = "rates", 
                                               names_prefix = "rate")
```

```{r}
rates_graph <- dep_rates_longer |> filter(is.na(value) == F) |> group_by(rates, private, value) |>
  summarise(n = n()) |> mutate(totalN = (cumsum(n)), percent = (n / sum(n)), per_100 = 100*percent) |>
  ungroup() |> mutate(satis = case_when(value == 1 ~ "Very dissatisfied",
                                        value == 2 ~ "Somewhat dissatisfied",
                                        value == 3 ~ "Somewhat satisfied",
                                        value == 4 ~ "Very satisfied")) |> 
  mutate(Type = ifelse(private == 1, "Private Center", "Public Center"))

```

```{r}
p1 <- ggplot(data=rates_graph |> filter(rates == "_water1"), aes(x=value, y=per_100, fill=Type)) +
geom_bar(stat="identity", position=position_dodge()) + 
  scale_fill_manual(values=c("red4",
                             "darkblue")) + theme_bw(base_size = 9) +
  ggtitle("How satisfied are you with the drinking water?") +
  labs(x = "", y = "Percentage")

p2 <- ggplot(data=rates_graph |> filter(rates == "_drain1"), aes(x=value, y=per_100, fill=Type)) +
geom_bar(stat="identity", position=position_dodge()) + 
  scale_fill_manual(values=c("red4",
                             "darkblue")) + theme_bw(base_size = 9) +
  ggtitle("How satisfied are you with the drainage?") +
  labs(x = "", y = "Percentage")

p3 <- ggplot(data=rates_graph |> filter(rates == "_toilet1"), aes(x=value, y=per_100, fill=Type)) +
geom_bar(stat="identity", position=position_dodge()) + 
  scale_fill_manual(values=c("red4",
                             "darkblue")) + theme_bw(base_size = 9) +
  ggtitle("How satisfied are you with the toilets?") +
  labs(x = "", y = "Percentage")

p4 <- ggplot(data=rates_graph |> filter(rates == "_shower1"), aes(x=value, y=per_100, fill=Type)) +
geom_bar(stat="identity", position=position_dodge()) + 
  scale_fill_manual(values=c("red4",
                             "darkblue")) + theme_bw(base_size = 9) +
  ggtitle("How satisfied are you with the showers?") +
  labs(x = "", y = "Percentage")

p5 <- ggplot(data=rates_graph |> filter(rates == "_goods1"), aes(x=value, y=per_100, fill=Type)) +
geom_bar(stat="identity", position=position_dodge()) +
  scale_fill_manual(values=c("red4",
                             "darkblue")) + theme_bw(base_size = 9) +
  ggtitle("How satisfied are you with the goods?") +
  labs(x = "", y = "Percentage")

p6 <- ggplot(data=rates_graph |> filter(rates == "_visits1"), aes(x=value, y=per_100, fill=Type)) +
geom_bar(stat="identity", position=position_dodge()) + 
  scale_fill_manual(values=c("red4",
                             "darkblue")) + theme_bw(base_size = 9) +
  ggtitle("How satisfied are you with your visits treatment?") +
  labs(x = "", y = "Percentage") 

p7 <- ggplot(data=rates_graph |> filter(rates == "_educ1"), aes(x=value, y=per_100, fill=Type)) +
geom_bar(stat="identity", position=position_dodge()) + 
  scale_fill_manual(values=c("red4",
                             "darkblue")) + theme_bw(base_size = 9) +
  ggtitle("How satisfied are you with the educational programs?") +
  labs(x = "", y = "Percentage")

p8 <- ggplot(data=rates_graph |> filter(rates == "_light1"), aes(x=value, y=per_100, fill=Type)) +
geom_bar(stat="identity", position=position_dodge()) + 
  scale_fill_manual(values=c("red4",
                             "darkblue")) + theme_bw(base_size = 9) +
  ggtitle("How satisfied are you with the lights?") +
  labs(x = "", y = "Percentage")

```

```{r}

p11 <- ggplot(data=rates_graph |> filter(rates == "_water1"), aes(x=value, y=per_100, fill=Type)) +
geom_bar(stat="identity", position=position_dodge()) + 
  scale_fill_manual(values=c("red4",
                             "darkblue")) +
  ggtitle("How satisfied are you with the drinking water?") +
  labs(x = "", y = "Percentage")

p22 <- ggplot(data=rates_graph |> filter(rates == "_drain1"), aes(x=value, y=per_100, fill=Type)) +
geom_bar(stat="identity", position=position_dodge()) + 
  scale_fill_manual(values=c("red4",
                             "darkblue"))  +
  ggtitle("How satisfied are you with the drainage?") +
  labs(x = "", y = "Percentage")
```



```{r}
p1
ggsave(paste0(path_results, "water_rates.jpeg"), width = 6.8, height = 6.2)
p2
ggsave(paste0(path_results, "drain_rates.jpeg"), width = 6.8, height = 6.2)
```

```{r}
fig2 <- ggarrange(p11, p22, 
          labels = c("A", "B"), common.legend = TRUE, legend = "bottom",
          ncol = 1, nrow = 2)

annotate_figure(fig2) |>
  ggexport(filename = paste0(path_results,"rates_contract.jpeg"))
fig2
```



```{r}
fig <- ggarrange(p3, p4, p5, p8, 
          labels = c("A", "B", "C", "D"), common.legend = TRUE, legend = "bottom",
          ncol = 2, nrow = 2) |> ggexport(filename = paste0(path_results,"rates_contract_4.jpeg"))
```


```{r}
tab(controls_final, private) |> select(private, n, totalN, percent) |> kbl(col.names = c("Type of Center",
                      "N", 
                      "Total", "Percentage"),
        format = "latex",
        caption = "Number of Observations per Group: Private and Public",
        booktabs = T)
  
```











