---
title: "Thesis_ENPOL"
author: "Eduardo Zago"
date: "22/3/2022"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,  fig.align = "center")
```

```{r, include=FALSE, echo=FALSE}
library(haven)
library(tidyverse)
library(sandwich)
library(stargazer)
library(fixest)
library(knitr)
```


```{r, include=FALSE}
# Paths
path_in <- "C:/Users/lalo-/Dropbox/Research/Prisons/Tesis/data/clean/"
path_out <- "C:/Users/lalo-/Dropbox/Research/Prisons/Tesis/data/clean/csvs/"
path_results <- "C:/Users/lalo-/Dropbox/Research/Prisons/Tesis/results/"
```

```{r, include=FALSE, warning=FALSE, echo=FALSE}
# Importing the data
datos <- read_dta(paste0(path_in, "ENPOL2021_fed.dta"))
```

Run to define the functions in memory:

```{r functions}
no_sabe_toNA <- function(x) ifelse(x == 8 | x == 9, NA, x)

no_responde_toNA <- function(x) ifelse(x == 99 | x == 98, NA, x)

tab <- function(frame_x, var_name){
     var_name <- enquo(var_name)
     frame_x |>
          group_by(!!var_name) |>
          summarise(n = n()) |>
          mutate(totalN = (cumsum(n)),
                 percent = round((n / sum(n)), 3),
                 cumuPer = round(cumsum(freq = n / sum(n)), 3))
}

dummies <- function(x) ifelse(x == 2, 0, x)
```


```{r, include = T, results='asis'}

table_prisons <- tab(datos1, NOM_INT) 

```

First of all we must define what are the possible dependent variables and the control variables. For the dependent variables we must look for questions that ask the inmates for characteristics of the prisons they are at. For example, corruption levels, quality of cells, basic services, activities, discrimination, etc. We also need controls, characteristics of the inmates such as employment and income history, prior housing condition, level of schooling, sexual orientation, gender identity, health conditions, crimes allegedly committed, marital status. An the main and most important variable is if they are in public or in private prisons (priv)

Let´s start with the prison characteristics:

Relevant: 

1. Type of prison: varonil 1, fem 2, mixed 3
2. Capacity: cap
3. State: NOM_ENT, CVE_ENT
4. Municipality: to be made
5. Margination index: to be made
6. Substance abuse treatment: P1_47 ----> treat_drugs
7. Condom supply: P1_48 ----> condoms


Inmates characteristics:

1. Time incarcerated (discrete): P1_1A ----> time_inc
2. Age (discrete): P1_3 -----> age
3. Nationality (cat): P1_4 ----> country
4. State (cat): P1_5 -----> state
5. Marital Status (cat): P1_7 -----> marital
6. Children under 18 (cat): P1_9 ------> children
7. Age children 1 (discrete): P1_10_1 ------> age_child1
8. Age children 2: P1_10_2 ------> age_child2
9. Age children 3: P1_10_3 ------> age_child3
10. Dialects (dummy): P1_12 ------> dialect 
11. Afroamerican 1/indigenous 2/other 3(cat): P1_15 -------> gen three dummies from here: afro, indig, other
12. Literacy, reading (dummy): P1_16 -----> lit_read
13. Literacy, writing (dummy): P1_17 -----> lit_write
14. Scholarity (cat): P1_18_N ------> schooling
15. Schooling grade (discrete): P1_18_G ----> school_grade
16. Health (dummies for kind of illness): 

Illness -->      Var -->   NewVar
Diabetes       P1_24_1    diabetes
Hypertension   P1_24_2    hypert
Cancer         P1_24_3    cancer
Neumonia       P1_25_4    neumonia
Tuberculosis   P1_24_5    tuber
Hepatitis      P1_24_6    hep
VIH            P1_24_7    vih
COVID19        P1_24_8    covid
Other          P1_24_9    ill_other

17. Substance Consumption (30 days)

Substance -->    Var -->   NewVar
Alcohol -->    P1_44_2    alcohol
Weed -->       P1_44_3    weed
Mona -->       P1_44_4    mona
LSD -->        P1_44_5    lsd
Mushrooms -->  P1_44_6    mushr
Cocaine -->    P1_44_7    cocaine1
Paste Coca->   P1_44_8    cocaine2
Crack -->      P1_44_9    crack
Heroine -->    P1_44_10   heroine
Morphine -->   P1_44_11   morphine
Antidepre -->  P1_44_12   antidep
meth -->       P1_44_13   meth
Other -->      P1_44_14   drug_other

Prior characteristics
18. State of residence: P2_1 ----> state_prior
19. Prior housing condition: P2_2 ----> housing_prior
20. Have you worked before?: P2_6 ----> work_dummy
21. Municipal detention: P3_4 ------> cve_muni_det
22. Date of detention: P3_5_A/P3_5_M/P3_5_A ---> date_det
23. Jail time (discrete) years: P5_4_A ----> sentence_y
24. Jail time (discrete) months: P5_4_M ----> sentence_m
25. Date of sentence: P5_5_M/P_5_A/01 ---> date_sentence
26. Crimes: Worked in another frame for now. P5_11_01:P5_13_9
27. Income (month prior to detention): P2_15 ---> income_prior
28. Food scarcity prior (dummy): P2_14_1 ----> scarce_f
29. Debt prior (dummy): P2_14_2 -----> debt
30. Gender Identity (cat): P1_22 ----> gender
40. Sexual Orientation (cat) P1_23 ---> sex_or



Possible Dependent Variables:

1. Suicide Thoughts (dummy): P1_29 -----> suicide_t
2. Suicide Attempts (dummy): P1_30 -----> suicide_a



```{r, include=F, warning=FALSE, echo=FALSE}
#Renaming the variables, first run
datos1 <- datos |> rename(time_inc = P1_1A, age = P1_3, country = P1_4,
                          state = P1_5, marital = P1_7, child = P1_8, children = P1_9,
                          agechild1 = P1_10_1, agechild2 = P1_10_2, agechild3 = P1_10_3,
                          dialect = P1_12, race = P1_15, lit_read = P1_16, lit_write = P1_17,
                          school = P1_18_N, school_grade = P1_18_G, diabetes = P1_24_1,
                          hypert = P1_24_2, cancer = P1_24_3, neumonia = P1_24_4, 
                          tuber = P1_24_5, hep = P1_24_6, hiv = P1_24_7, covid = P1_24_8,
                          ill_other = P1_24_9, alcohol = P1_44_2, weed = P1_44_3,
                          mona = P1_44_4, lsd = P1_44_5, mushr = P1_44_6, cocaine1 = P1_44_7,
                          cocaine2 = P1_44_8, heroine = P1_44_9, morphine = P1_44_10, 
                          antidep = P1_44_11, meth = P1_44_12, drug_other = P1_44_13, 
                          state_prior = P2_1, housing_prior = P2_2, work_dummy = P2_6,
                          cve_muni_det = P3_4, sentence_y = P5_4_A, sentence_m = P5_4_M, 
                          income_prior = P2_15, scarce_food = P2_14_1, debt = P2_14_2, 
                          gender = P1_22, sex_or = P1_23, treat_drugs = P1_47,
                          condom = P1_48, re_offender = P9_1)

# COVID, Neumonía treatment

datos1 <- datos1 |> rename(neumonia_t = P1_26_4, covid_t = P1_26_8)

# Drugs 12 months

datos1 <- datos1 |> rename(cocaine1_12 = P1_43_7, cocaine2_12 = P1_43_8, 
                           crack_12 = P1_43_9, heroine_12 = P1_43_10,
                           morphine_12 = P1_43_11,
                           meth_12 = P1_43_13, weed_12 = P1_43_3, 
                           mona_12 = P1_43_4)
```

```{r}
Women_tab <- tab(datos1 |> filter(mujer == 1) |>
                   select(ID_PER, mujer, private), private) |>
  select(private, n, totalN)
```

Given that there are no public prisons for women for comparison, we restrict our analysis to private versus public male prisons.

```{r}
datos1 <- datos1 |> filter(mujer==0) |> select(-c(mujer, COD_RES))
```


```{r cleancon, include=F, warning=FALSE, echo=FALSE}
controls <- datos1 |> select(ID_PER, private, time_inc, age, country, state, marital, child,
                             children, 
                             agechild1, agechild2, agechild3, dialect, race, 
                             lit_read, lit_write, school, school_grade,
                             diabetes, hypert, cancer, neumonia, neumonia_t, tuber, hep, 
                             hiv, covid, covid_t, 
                             ill_other, alcohol, weed_12, mona_12, lsd, mushr, cocaine1_12,
                             cocaine2_12, heroine_12, morphine_12, antidep, meth_12, drug_other, 
                             state_prior, housing_prior, work_dummy, cve_muni_det, sentence_y, 
                             sentence_m, income_prior, scarce_food, debt, gender, sex_or, re_offender) 

```


```{r}
tab(controls, diabetes)
tab(controls, sentence_y)
tab(controls, sentence_m)
```

Cleaning "No sabe, no responde" to NA

```{r cat}

controls_cat <- controls |> select(ID_PER, private, age, school, school_grade, 
                                   state, agechild1:agechild3,
                                   state_prior, sentence_m, sentence_y, 
                                   housing_prior, children) |> 
     mutate(across(where(is.numeric), no_responde_toNA))

```

Check:
```{r}
tab(controls_cat, school)
tab(controls_cat, children)
```



```{r}
control_dummies <- controls |> select(-c(private, age, school, school_grade, state, 
                                      agechild1, agechild2, agechild3,
                                      state_prior, sentence_m, sentence_y, cve_muni_det, housing_prior,
                                      children)) |> 
     mutate(across(where(is.numeric), no_sabe_toNA))
     
```

```{r prueba3}
tab(control_dummies, child)
tab(control_dummies, re_offender)
```

Now, for the dummies we would like to change the number 2 to a 0. 

```{r dumm}

control_dummies <- control_dummies |> 
  mutate(across(c("child", "dialect", "scarce_food", "debt", "re_offender"), 
                                                    dummies)) |> 
     mutate(across(c(8:33), dummies))

```

```{r prueba4}
tab(control_dummies, lsd)
tab(control_dummies, mushr)
tab(control_dummies, heroine_12)
tab(control_dummies, cocaine1_12)
tab(control_dummies, re_offender)

```


Generating some other variables from the dummies, such as and dropping non-informative variables such as LSD and Mushrooms who only have 2 respondents:

1) Sick dummy
2) For the drug abuse in the last 30 days questions, most respondents decided not to answer and left the question in blank (possible acceptation bias). Given this, I decided to use the twelve month question for hard drugs (cocaine, heroine, meth, etc.) and to generate two dummies out of these variables: 1) $HardDrugs_i$ which is 1 if the respondent answered that he has consumed hard drugs in the last twelve months and 0 in any other case. 2) $Drugs_i$ which is 1 if the respondent has consumed alcohol, weed, antidepressants in the last month and 0 in any other case. 

```{r}
# Drugs

control_dummies <- control_dummies |> select(-c(lsd, mushr)) |> 
     mutate(HardDrugs = if_else(cocaine1_12 == 1 | cocaine2_12 == 1 | heroine_12 == 1 | 
                                    morphine_12 == 1 | meth_12 == 1, 1, 0)) |>
     mutate(Drugs = if_else(alcohol == 1 | weed_12 == 1 | mona_12 == 1, 1, 0)) |> 
     mutate(HardDrugs = if_else(is.na(HardDrugs) == T, 0, HardDrugs),
            Drugs = if_else(is.na(Drugs) == T, 0, Drugs))


tab(control_dummies, HardDrugs)
tab(control_dummies, Drugs)
```


Now from the categorical let's generate 
1) Afroamerican 1/indigenous 2/other 3(cat): P1_15 -------> gen three dummies from here: afro, indig, other

```{r}
control_dummies <- control_dummies |> mutate(afro = ifelse(race == 1, 1, 0), indig = ifelse(race == 2, 1, 0),
                                             other = ifelse(race == 3, 1, 0)) |> 
  mutate(afro = ifelse(is.na(race) == T, NA, afro), other = ifelse(is.na(race) == T, NA, other),
         indig = ifelse(is.na(race) == T, NA, indig)) 

tab(control_dummies, afro)
tab(control_dummies, indig)
tab(control_dummies, race)
```

Now for the categoricals: 

1) Sentence = sentence_y + sentence_m / 12
2) Age squared

```{r}
controls_cat <- controls_cat |> mutate(sentence_m = ifelse(sentence_m == 97, 0, sentence_m)) |> 
  mutate(sentence = sentence_y + sentence_m/12) |> 
  mutate(sentence = ifelse(is.na(sentence_y) == T & is.na(sentence_m) == F, sentence_m/12, sentence)) |>
  mutate(age_squared = age*age)

controls_cat <- controls_cat |> left_join(control_dummies |> select(ID_PER, child), by = "ID_PER") |> 
  mutate(children = ifelse(child == 0, 0, children))
```

And we join the characteristics again:

```{r}
controls_final_full <- controls_cat |> left_join(control_dummies |> select(-child), by = "ID_PER") |>
  left_join(controls |> select(ID_PER, cve_muni_det) |> 
              mutate(cve_muni_det = ifelse(cve_muni_det == 999, NA, cve_muni_det)), by = "ID_PER")

# Order it
controls_final <- controls_final_full |> select(ID_PER, country, state, state_prior, cve_muni_det, private, age, gender, 
                                           sex_or, afro, indig, other, school, child, children, 
                                           agechild1:agechild3, marital, dialect, lit_read, lit_write,
                                           diabetes:neumonia, tuber:covid, HardDrugs, Drugs,
                                           time_inc, sentence, re_offender,
                                           work_dummy, income_prior, scarce_food, debt, housing_prior, race)

```


Generating dummies from categorical variables (sex or, gender, marital status)

```{r}
controls_final <- controls_final |> mutate(cis = ifelse(gender == 1, 1, 0), 
                                           trans = ifelse(gender == 3 | gender == 4, 1, 0),
                                           other_gender = ifelse(gender == 5, 1, 0),
                                           bi = ifelse(sex_or == 1, 1, 0),
                                           gay = ifelse(sex_or == 2, 1, 0),
                                           hetero = ifelse(sex_or == 3, 1, 0),
                                           other_sexor = ifelse(sex_or == 4, 1, 0),
                                           married = ifelse(marital == 4, 1, 0),
                                           free_union = ifelse(marital == 1, 1, 0),
                                           single = ifelse(marital == 5, 1, 0), 
                                           divorced = ifelse(marital == 6, 1, 0),
                                           separated = ifelse(marital == 2 | marital == 3, 1, 0),
                                           widower = ifelse(marital == 7, 1, 0))

controls_final <- controls_final |> rename(other_race = other)
```

```{r}
tab(controls_final, marital)
tab(controls_final, free_union)
tab(controls_final, married)
```


```{r}
write.csv(controls_final, paste0(path_out, "controls.csv"), row.names = F)
```


Dependent Variables:

Possible Outcomes:

1. Suicide Thoughts (dummy): P1_29 -----> suicide_t
2. Suicide Attempts (dummy): P1_30 -----> suicide_a
3. Corruption: corruption_t = P7_41_2, corruption_quant = P8_3 89
4. Food : quant_food = P6_14_1, qual_food = P6_14_2, sick_food = P6_14_3
5. Violence: insecure = P7_36, violence_t = P7_41_4, rape_t = P7_45_4

Reinsertion activities:

1. Studying dep_study = P7_18
2. Visiting: (dummy) dep_visit = P7_25, (times) dep_t_visit = P7_27

Satisfaction rates: (possible source of bias: type of person, maybe they are more prone to give high ratings when asked, or are more neutral than other people. We could solve this by obtaining the mean of the reviews of several goods and services from the same individual and subtracting it from each rating)

1) Water P6_9_1 ----> rate_water
2) Drainage P6_9_2 ----> rate_drain
3) Light P6_9_3 -----> rate_light
4) Shower P6_9_4 ----> rate_shower
5) Toilet P6_9_5 ----> rate_toilet
6) Basic Goods rate_goods = P6_11
7) Spaces rate_space = P7_8
8) Education rate_educ = P7_21
9) Visitas: rate_visits = P7_34


```{r}
datos1 <- datos1 |> rename(rate_water = P6_9_1, rate_drain = P6_9_2, rate_visits = P7_34,
                           rate_light = P6_9_3, rate_shower = P6_9_4, 
                           rate_toilet = P6_9_5, rate_goods = P6_11, rate_educ = P7_21,
                           rate_space = P7_8, dep_visit = P7_25,
                           quant_food = P6_14_1, qual_food = P6_14_2, sick_food = P6_14_3,
                           dep_t_visit = P7_27, dep_study = P7_18, 
                           insecure = P7_36, violence_t = P7_41_4, rape_t = P7_45_4,
                           corruption_t = P7_41_2, corruption_quant = P8_3, suicide_t = P1_29, suicide_a = P1_30)
```


Dividing the dependent variables in Sections

```{r}

dep_outcomes <- datos1 |> select(ID_PER, private, suicide_t, suicide_a, insecure,
                                 violence_t, rape_t, quant_food, qual_food, sick_food, dep_visit, dep_t_visit,
                                 dep_study, corruption_t, corruption_quant)

dep_rates <- datos1 |> select(ID_PER, private, rate_water, rate_drain, rate_visits, rate_light, rate_shower,
                              rate_toilet, rate_goods, rate_educ) |> 
  mutate(across(where(is.numeric), no_sabe_toNA))

```


Working with the rating of the individuals:

Getting each individual mean and the group mean:


Recoding the rates: 1 --> 4 2 --> 3, 3 ---> 2 and 4 ---> 1

```{r}
dep_rates <- dep_rates |> mutate(rate_water1 = case_when(rate_water == 1 ~ 4,
                                                         rate_water == 2 ~ 3,
                                                         rate_water == 3 ~ 2,
                                                         rate_water == 4 ~ 1,
                                                         is.na(rate_water) == T ~ rate_water)) |>
  mutate(rate_drain1 = case_when(rate_drain == 1 ~ 4,
                                 rate_drain == 2 ~ 3,
                                 rate_drain == 3 ~ 2,
                                 rate_drain == 4 ~ 1,
                                 is.na(rate_drain) == T ~ rate_drain)) |>
  mutate(rate_visits1 = case_when(rate_visits == 1 ~ 4,
                                  rate_visits == 2 ~ 3,
                                  rate_visits == 3 ~ 2,
                                  rate_visits == 4 ~ 1,
                                  is.na(rate_visits) == T ~ rate_visits)) |> 
  mutate(rate_light1 = case_when(rate_light == 1 ~ 4,
                                 rate_light == 2 ~ 3,
                                 rate_light == 3 ~ 2,
                                 rate_light == 4 ~ 1,
                                 is.na(rate_light) == T ~ rate_light)) |>
  mutate(rate_shower1 = case_when(rate_shower == 1 ~ 4,
                                  rate_shower == 2 ~ 3,
                                  rate_shower == 3 ~ 2,
                                  rate_shower == 4 ~ 1,
                                  is.na(rate_shower) == T ~ rate_shower)) |>
  mutate(rate_toilet1 = case_when(rate_toilet == 1 ~ 4,
                                 rate_toilet == 2 ~ 3,
                                 rate_toilet == 3 ~ 2,
                                 rate_toilet == 4 ~ 1,
                                 is.na(rate_toilet) == T ~ rate_toilet)) |>
  mutate(rate_light1 = case_when(rate_light == 1 ~ 4,
                                 rate_light == 2 ~ 3,
                                 rate_light == 3 ~ 2,
                                 rate_light == 4 ~ 1,
                                 is.na(rate_light) == T ~ rate_light)) |> 
  mutate(rate_toilet1 = case_when(rate_toilet == 1 ~ 4,
                                 rate_toilet == 2 ~ 3,
                                 rate_toilet == 3 ~ 2,
                                 rate_toilet == 4 ~ 1,
                                 is.na(rate_toilet) == T ~ rate_toilet)) |>
  mutate(rate_goods1 = case_when(rate_goods == 1 ~ 4,
                                 rate_goods == 2 ~ 3,
                                 rate_goods == 3 ~ 2,
                                 rate_goods == 4 ~ 1,
                                 is.na(rate_goods) == T ~ rate_goods)) |>
  mutate(rate_educ1 = case_when(rate_educ == 1 ~ 4,
                                 rate_educ == 2 ~ 3,
                                 rate_educ == 3 ~ 2,
                                 rate_educ == 4 ~ 1,
                                 is.na(rate_educ) == T ~ rate_educ))
  
```

```{r}
# Checking

tab(dep_rates, rate_water)
tab(dep_rates_2, rate_water1)

tab(dep_rates, rate_drain)
tab(dep_rates_2, rate_drain1)
```



```{r}
dep_rates_2 <- dep_rates |> select(ID_PER, private, rate_water1:rate_educ1)
```



```{r}
write.csv(dep_rates_2, paste0(path_out, "dependent_rates.csv"), row.names = F)
write.csv(dep_rates, paste0(path_out, "dependent_rates1.csv"), row.names = F)
```

Let's start graphing some results:

```{r}
rates_graph <- dep_rates_longer |> filter(is.na(value) == F) |> group_by(rates, private, value) |>
  summarise(n = n()) |> mutate(totalN = (cumsum(n)), percent = (n / sum(n)), per_100 = 100*percent) |>
  ungroup() |> mutate(satis = case_when(value == 1 ~ "Very satisfied",
                                        value == 2 ~ "Somewhat satisfied",
                                        value == 3 ~ "Somewhat dissatisfied",
                                        value == 4 ~ "Very dissatisfied")) |> 
  mutate(Type = ifelse(private == 1, "Private Center", "Public Center"))

```



Dependent Outcomes:

```{r}
tab(dep_outcomes, suicide_t)
tab(dep_outcomes, suicide_a)
tab(dep_outcomes, corruption_quant)
```

```{r}

dep_outcomes <- dep_outcomes |> mutate(across(c(3:13), dummies)) |> 
  mutate(across(c(3:13), no_sabe_toNA))

dep_outcomes <- dep_outcomes |> mutate(suicide_a = ifelse(is.na(suicide_a) == T, 0, 1))
```


Crimes sentenced:


P5_11_01 -----> P5_13_9 

```{r}
crimes <- datos |> select(ID_PER, private, P5_11_01:P5_13_9) 
```

Renaming some variables

```{r}
crimes <- crimes |> rename(pos_drugs = P5_11_08, com_drugs = P5_11_09, 
                           hom_culp = P5_11_11, hom_dol = P5_11_12,
                           guns = P5_11_13, kidnap = P5_11_17, 
                           rape = P5_11_18, org_crime = P5_11_20,
                           org_crime_rob = P5_12_01, org_crime_kid = P5_12_02,
                           org_crime_hom = P5_12_03, org_crime_drug = P5_12_04,
                           org_crime_trata = P5_12_05, org_crime_gun = P5_12_07,
                           crime_fed = P5_13_1, crime_state = P5_13_2) |> 
  select(ID_PER, private, pos_drugs, com_drugs, hom_culp, hom_dol, guns, 
         kidnap, rape, org_crime, org_crime_rob, org_crime_kid, org_crime_hom, 
         org_crime_drug, org_crime_trata, org_crime_gun, crime_fed, crime_state)
```

Descriptive statistics

```{r}
tab(crimes, pos_drugs)
tab(crimes, hom_dol)
tab(crimes, org_crime_drug)
```



```{r}
crimes <- crimes |> mutate(drug_related = com_drugs) |> 
  mutate(drug_related = if_else(pos_drugs == 1, 1, drug_related)) 

crimes <- crimes |> mutate(drug_related = ifelse(org_crime_drug == 1 & is.na(org_crime_drug) == F, 1, drug_related))

tab(crimes, drug_related)
```

```{r}
crimes <- crimes |> mutate(hom_related = hom_culp) |> 
  mutate(hom_related = if_else(hom_dol == 1, 1, hom_related)) 

crimes <- crimes |> mutate(hom_related = ifelse(org_crime_hom == 1 & is.na(org_crime_hom) == F, 1, hom_related))

tab(crimes, hom_related)
```

```{r}
crimes <- crimes |> mutate(guns_related = guns)

crimes <- crimes |> mutate(guns_related = ifelse(org_crime_gun == 1 & is.na(org_crime_gun) == F, 1, guns_related))

tab(crimes, guns_related)
```

```{r}
crimes <- crimes |> mutate(kidnap_related = kidnap)

crimes <- crimes |> mutate(kidnap_related = ifelse(org_crime_kid == 1 & is.na(org_crime_kid) == F, 1, kidnap_related))

crimes <- crimes |> mutate(kidnap_related = ifelse(org_crime_trata == 1 & is.na(org_crime_trata) == F, 1, kidnap_related))

tab(crimes, kidnap_related)
```

Final dataset Crimes: Now, the question is: Were you sentenced for ---- crime? 1 - yes 0 - Not answered as yes. So in this case I'm going to code NAs to 0, thus these variables will not reduce the sample and would just be proxies of crime presence for each group, not the actual statistics of crimes.

```{r}
crimes <- crimes |> select(ID_PER, private, rape, drug_related, hom_related, guns_related,
                           kidnap_related, org_crime)
```

```{r}
na_to_zero <- function(x) ifelse(is.na(x)==T, 0, x)
```

```{r}
crimes <- crimes |> left_join(crimes |> select(-private) |> 
                                mutate(across(where(is.numeric), na_to_zero)), by = "ID_PER")
```

```{r}
write.csv(crimes, paste0(path_out, "crimes.csv"), row.names = F)
```


Merging both bases with the controls to run final regressions:

```{r}
base_final <- dep_outcomes |> left_join(dep_rates_2 |> select(-private), by = "ID_PER") |> 
  left_join(controls_final |> select(-private), by = "ID_PER") |> 
  left_join(datos1 |> select(ID_PER, CVE_ENT), by = "ID_PER") |> 
  left_join(crimes |> select(-private), by = "ID_PER")
```

```{r}
#write.csv(dep_outcomes, paste0(path_out, "dependent_outcomes.csv"), row.names = F)
write.csv(base_final, paste0(path_out, "base_final.csv"), row.names = F)
```





